Learned image compression

### 2023-03-20 paper/paper.tex
Fig figures.
* added a paragraph in results section

In Figure a, we demonstrate the reconstruction performance of the four models trained with different parameters.

@@

\vfill

\begin{figure}[h!]
\begin{minipage}[b]{0.8\linewidth}
    \centering
    \includegraphics[width=7.2cm]{kodak_fixed.png}
    \centerline{(a) Average values over KODAK dataset \cite{kodak}.}\medskip
\end{minipage}
\begin{minipage}[b]{0.8\linewidth}

    \centering
    \includegraphics[width=7.2cm]{kodak_per_fixed.png}
    \centerline{(b) Performance on individual images of KODAK dataset \cite{kodak}.}\medskip
\end{minipage}
    \label{fig:results}
    \caption{Results on KODAK dataset \cite{kodak}.}
\end{figure}

>>>>

In Fig 2, we demonstrate the reconstruction performance of the four models trained with different parameters. We can see we're neck-in-neck with the conventional approaches for low bpp rates. And Fig 3a. we observed Model 4, has better sharpness but suffers from glitch effect in uniform backgrounds.

@@

\begin{figure}[h!]
\begin{minipage}[b]{0.8\linewidth}
    \centering
    \includegraphics[width=7.2cm]{kodak_fixed.png}
    \centerline{(a) Average values.}\medskip
\end{minipage}
\begin{minipage}[b]{0.8\linewidth}

    \centering
    \includegraphics[width=7.2cm]{kodak_per_fixed.png}
    \centerline{(b) Performance on individual images.}\medskip
\end{minipage}
    \label{fig:results}
    \caption{Results on KODAK dataset \cite{kodak}.}
\end{figure}
